Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-09-05 sections/3algebras.tex
Finished writting up lem:Lan_preserve_colim and prepared main_theorem.tex that encapsulates the main definitions and results.

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for (locally constant) factorization algebras. We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not. We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case. To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps. First we have the following results:
%
\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
\end{proposition}
%
\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

@@

The following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
%
\begin{lemma}\label{lem:Lan_preserve_colim}
    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of (locally small) $\infty$-categories, where $\mathscr{M}$ and $\catC$ are cocomplete. Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$. $L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
    %
    \begin{align}
        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
    \end{align}
    %
    does so.
\end{lemma}

\begin{proof}
    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$. We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
    %
    \begin{equation}
        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
    \end{equation}
    %
    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
    %
    \begin{align}
        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
    \end{align}
    %
    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds

    {\color{red} Proof of being adjoint}

    In the general situation where $\iota$ is not necessarily the Yoneda embedding we can partially reduce to the previous case because we can write
    %
    \begin{equation}
        L_{\iota} F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota} y_{\mathscr{D}}.
    \end{equation}
    %
    Namely, this is because we know that $L_{y_{\mathscr{D}}} F$ preserves colimits, and by the assumptions in the lemma, $L_{\iota} F$ and $L_{\iota} y_{\mathscr{D}}$ are computed pointwise, as colimits over the same indexing $\infty$-category.

    Finally, we claim that there is an equivalence of functors
    %
    \begin{equation}
        \Big( L_{\iota} y_{\mathscr{D}} \simeq T_{\iota} \Big) \in \mathsf{Fun}(\mathscr{M}, \mathsf{PShv}(\mathscr{D})) 
    \end{equation}

    {\color{red} Proof of functor equivalence}

\end{proof}

>>>>

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras, locally constant or not. We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not. We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case. To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps. First we have the following results:
%
\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
\end{proposition}
%
\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

@@

The following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
%
\begin{lemma}\label{lem:Lan_preserve_colim}
    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of $\infty$-categories, where $\mathscr{D}$ is essentially small, while $\mathscr{M}$ and $\catC$ are locally small and cocomplete. Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$. $L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
    %
    \begin{align}
        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
    \end{align}
    %
    does so.
\end{lemma}

\begin{proof}
    We use the standard notation $y_{\mathscr{X}}=h_\bullet\colon\mathscr{X}\to\mathsf{PShv}(\mathscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mathscr{X}$ (see \cite[\href{https://kerodon.net/tag/03NF}{03NF},\href{https://kerodon.net/tag/03N2}{03N2}]{lurie_kerodon}). First, note that a left Kan extension of type
    %
    \begin{equation}
        L_{y_{\mathscr{D}}}F \colon \mathsf{PShv}(\mathscr{D}) \xrightarrow{\ \ \ \ } \mathscr{C}
    \end{equation}
    %
    preserves colimits as a consequence of \cite[\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon}. Next, we claim that there is an equivalence
    %
    \begin{equation}\label{WZUZC5F}
        L_{\iota}F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}
    \end{equation}
    %
    as functors $\mathscr{M} \to \mathscr{C}$. Indeed, consider the diagram
    % 
    \begin{equation}
        \begin{tikzcd}[sep = large]
            & \mathscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mathscr{D}}}"]\\
            \mathscr{M}\ar[rr,bend right=40,"{L_{\iota}F}"']\ar[r,"{L_{\iota}y_{\mathscr{D}}}"'] &[4em] \mathsf{PShv}(\mathscr{D})\ar[r,"{L_{y_{\mathscr{D}}}F}"'] & \mathscr{C},
        \end{tikzcd}
    \end{equation}
    %
    and note that by \cite[\href{https://kerodon.net/tag/03W9}{03W9},\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon} there is an equivalence (actually even an isomorphism) $L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}} \simeq F$ which commutes the right triangle. Consequently, using \cite[\href{https://kerodon.net/tag/02YH}{02YH}]{lurie_kerodon}, we have $L_{\iota}F \simeq L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})$. Since $L_{y_{\mathscr{D}}}F$ preserves colimits, we have $L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})\simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}$, obtaining \Cref{WZUZC5F}.

    Finally, we claim
    %
    \begin{equation}\label{D9NQYMT}
        L_{\iota}y_{\mathscr{D}} \simeq T_{\iota} := \iota^* \circ y_{\mathscr{M}}
    \end{equation}
    %
    as functors $\mathscr{M} \to \mathsf{PShv}(\mathscr{D})$, which will imply the Lemma by \Cref{WZUZC5F}. By \cite[\href{https://kerodon.net/tag/03WN}{03WN}]{lurie_kerodon} we have the following diagram in which the triangle commutes
    %
    \begin{equation}
        \begin{tikzcd}
            \mathscr{M} \arrow[r, "y_{\mathscr{M}}"] & \mathsf{PShv}(\mathscr{M}) \arrow[r, "\iota^*"] \arrow[d, "\top", phantom, very near start] & \mathsf{PShv}(\mathscr{D}) \arrow[ll, "H", bend left] \\
            & {} & \mathscr{D} \arrow[u, "y_{\mathscr{D}}"'] \arrow[llu, "\iota", bend left]
            \end{tikzcd},
    \end{equation}
    %
    so that $H$ is a left adjoint to $\iota^* \circ y_{\mathscr{M}}$. Being a right adjoint, we can write $\iota^* \circ y_{\mathscr{M}}$ as a left Kan extension, which allows for the following calculation
    %
    \begin{equation}
        \iota^* \circ y_{\mathscr{M}} \simeq L_{H}\mathrm{id}_{\mathsf{PShv}(\mathscr{D})} \simeq L_{H}(L_{y_{\mathscr{D}}} y_{\mathscr{D}}) \simeq L_{H \circ y_{\mathscr{D}}}(\mathscr{D}) \simeq L_{\iota}(y_\mathscr{D}),
    \end{equation}
    %
    where for the second equivalence we used the fact that $y_{\mathscr{D}}$ is a dense functor \cite[\href{https://kerodon.net/tag/03W2}{03W2}]{lurie_kerodon} (using the definition of dense functor as in \cite[\href{https://kerodon.net/tag/03VP}{03VP}]{lurie_kerodon}) and in the third equivalence we used \cite[\href{https://kerodon.net/tag/031M}{031M}]{lurie_kerodon}.
\end{proof}
